%
% ---------------------------------------------------
%
% Trabajo de Final de Grado:
% Author: Gonzalo Jesús García Martín <dracoyue@gmail.com>
% Capítulo: Fases
% Fichero: Cap9_Cap8English.tex
%
% ----------------------------------------------------
%

\cleardoublepage
\chapter{Conclusions and Future works}
\label{chap:futureLines}

	This chapter reviews different ways to enhance \CollegeApp, since every application must be willing to be improved. It will also discuss the conclusions and lessons learned along the realization of this project that has been especially rewarding.

	\section{Future works}
	
		Use cases that have not been implemented when creating the application behold. Some profiles are sorted according to their difficulty:
		
		\begin{itemize}
			\item Parents with children in different schools: At some point, students with the same parent or guardian attend different schools.
			\item Users with different profiles on the same school, for example, a school teacher in the school that your child attends.
			\item Teachers working in more than one school: In this case teachers to teach classes in more than one school will be contemplated.
		\end{itemize}
		
		Other features will also be envisaged, these are sorted according to their difficulty of implementation:
		
		\begin{itemize}
			\item Finding contacts.
			\item Sending report cards.
			\item Sending files through the application.
		\end{itemize}
	
	\section{Conclusions}
		The realization of this project will apply the expertise gained during the years of study, allowing real assimilation of the necessary skills and acquire new knowledge.
		This experience discloses the level of involvement that involves creating a fully functional application in a real environment. The analysis of other similar applications can realize the state of the market for the type of application built.
		
		\bigskip
		An application program may seem simple, but it takes dedication, time and hard work.